combo1

### 2024-04-02 Sections/Discussion.qmd
re-render manuscript

Here is a proposed outline for the Discussion section of the manuscript, based on the information provided:

@@

*Limitations*
- amount of training
- constant group always having more experience at nearest position
- constant group having more extrapolation items
- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general. 
- no mechanism to account for sequence effects in models
- more rigorous model comparison to account for exams greater complexity
- knowledge of function

>>>>

@@

*Limitations*
- amount of training

- constant group always having more experience at nearest position

- constant group having more extrapolation items

- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general.

- no mechanism to account for sequence effects in models

- more rigorous model comparison to account for exams greater complexity

- knowledge of function
